Gaps in stellar streams as a result of globular cluster fly-bys

### 2024-12-05 paper/main.tex
more changes
added Ishchenko citation for 5 gyr orbit integration choice

@@

      \item Once the positions and velocities of the entire globular cluster system, as to 5~Gyr ago, are found, we sample Palomar~5 with  100,000 particles which follow a Plummer distribution of mass and half-mass radius as in the Baumgardt catalogue.  We then integrate the evolution of these particles forward in time to the present day, by taking into account that each particle feels the gravitational potential of the Galaxy, that of its host cluster, and that of all the other clusters in the Galaxy. Note that we do not take into account self-gravity among particles. The particles expereince the gravitational field yet do not contribute to it. The equation of motion of a generic particle among the 100,000 which populate Pal~5 is thus: 
    \begin{equation}
      \ddot{\vec{r}}_p = -\nabla \Phi(R_p,z_p) + \left.\sum_{j}^{N_{GC}} \frac{Gm_j}{\left(|\vec{r}_j(t) - \vec{r}_p|^2 + b_j^2\right)^{3/2}}\right. \left(\vec{r}_j(t)- \vec{r}_p\right),
      \end{equation} \label{eq:equation_of_motion_particle} where the index $p$ represents one of the 100,000 particles of interest, $\vec{r_p}$ being its position, and $j$ indexes over the globular clusters as in Eq.~\ref{eq:GCNBody}.

>>>>

    Lastly, we select an integration time of 5 Gyr as a compromise between maximizing interaction statistics and adhering to the assumption that the galaxy can be modeled as a time-independent, constant mass distribution. \citet{2023A&A...673A.152I} analyzed the orbits of the Galactic cluster population using the same initial conditions as in this work, within five live Milky Way-like potentials from IllustrisTNG \citep{2018MNRAS.473.4077P}. They found that in all sampled potentials, orbital changes remain minimal over 5 Gyr, becoming significant only at earlier look-back times when the host galaxy had significantly less mass or was undergoing a merger event.

@@

      \item Once the positions and velocities of the entire globular cluster system, as to 5~Gyr ago, are found, we sample Palomar~5 with  100,000 particles which follow a Plummer distribution of mass and half-mass radius as in the Baumgardt catalogue.  We then integrate the evolution of these particles forward in time to the present day, by taking into account that each particle feels the gravitational potential of the Galaxy, that of its host cluster, and that of all the other clusters in the Galaxy. Note that we do not take into account self-gravity among particles. The particles expereince the gravitational field yet do not contribute to it. The equation of motion of a generic particle among the 100,000 which populate Pal~5 is thus: 
      \begin{equation}
        \ddot{\vec{r}}_p = -\nabla \Phi(R_p,z_p) + \left.\sum_{j}^{N_{GC}} \frac{Gm_j}{\left(|\vec{r}_j(t) - \vec{r}_p|^2 + b_j^2\right)^{3/2}}\right. \left(\vec{r}_j(t)- \vec{r}_p\right),
      \end{equation} \label{eq:equation_of_motion_particle} where the index $p$ represents one of the 100,000 particles of interest, $\vec{r_p}$ being its position, and $j$ indexes over the globular clusters as in Eq.~\ref{eq:GCNBody}. Note in that Eq.~\ref{eq:equation_of_motion_particle} the positions of the globular clusters are time-dependent since they are being loaded during this step and not computed.
